Deep Multimodal Generative Models for Weakly-Supervised Learning

### 2017-10-21 paper/draft.tex
Added more text

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{nips_2017}
\usepackage{graphicx}
\usepackage{natbib}

@@

\subsection{Multimodal Variational Autoencoders}
\subsection{Bidirectional Inference}

\section{Experiments}
TODO

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{nips_2017}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{natbib}

@@

\subsection{Multimodal Variational Autoencoders}
Given a dataset $(X, W) = \{ (x_{1,1}, x_{2,1}), ..., (x_{1,N}, x_{2,N}) \}$, where $x_{1}$ and $x_{2}$ are two modalities of possibly different dimensions. We assume that $x_{1}$ and $x_{2}$ are conditionally independent on the latent state $z$. Figure \ref{fig:diagram:graph} shows the graphical model of the generative process: $z \sim p(z)$ and $x_{1}, x_{2} \sim p(x_{1}, x_{2} | z)$.

We can estimate the lower bound of the log-likelihood $\textup{log }p(x_{1}, x_{2})$ as follows:

\begin{equation}
\textup{log }p(x_{1}, x_{2}) \geq E_{q_{\theta}(z | x_{1}, x_{2})}[\textup{log }\frac{p_{\theta}(x_{1}, x_{2}, z)}{q_{\phi}(z | x_{1}, x_{2})}]
\end{equation}

\begin{multline}
\textup{log }p(x_{1}, x_{2}) \geq -D_{KL}(q_{\phi}(z | x_{1}, x_{2}) || p(z)) \\ + E_{q_{\phi}(z | x_{1}, x_{2})}[\textup{log } p_{\theta_{x_{1}}}(x_{1} | z)] + E_{q_{\phi}(z | x_{1}, x_{2})}[\textup{log } p_{\theta_{x_{2}}}(x_{2} | z)]
\end{multline}

The equation above has two reconstruction terms, one for each modality. As with VAEs, we have $q_{\theta}(z | x_{1}, x_{2})$. as the encoder and $p_{\theta_{x_{1}}}(x_{1} | z)$ and $p_{\theta_{x_{2}}}(x_{2} | z)$ as decoders.

\begin{figure}[!h]
\centering
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=.75\linewidth]{graph.pdf}
        \caption{}
        \label{fig:diagram:graph}
    \end{subfigure}\hspace{5mm}
    \begin{subfigure}[b]{.10\linewidth}
        \includegraphics[width=.75\linewidth]{modelv2}
        \caption{}
        \label{fig:diagram:modelv2}
    \end{subfigure}\hspace{5mm}
    \begin{subfigure}[b]{.10\linewidth}
        \includegraphics[width=.75\linewidth]{modelv1}
        \caption{}
        \label{fig:diagram:modelv1}
    \end{subfigure}\hspace{5mm}
    \begin{subfigure}[b]{.15\linewidth}
        \includegraphics[width=.75\linewidth]{modelv3}
        \caption{}
        \label{fig:diagram:modelv3}
    \end{subfigure}
    \caption{(a) Graphical model of the MMVAE. Gray circles represent observed variables. The white circles represent latent variables. (b) MMVAE when modality 2 is missing. When only 1 modality is present, we ignore the PoG (product of Gaussians). (c) MMVAE when modality 1 is missing. (d) MMVAE when both modalities exist. $E_{1}$ and $E_{2}$ represent the two encoders: $q_{\phi_{x_{1}}}(z | x_{1})$ and $q_{\phi_{x_{2}}}(z | x_{2})$. Regardless if modalities are missing, we optimize the parameters of $E_{1}$ and $E_{2}$.}
    \label{fig:diagram}
\end{figure}
